Gammapy: A Python package for gamma-ray astronomy

### 2022-12-07 src/ms-review.tex
Split section 2 in two subsections

In the most general way we can write the expected number of detected events at measured
position $p$ and energy $E$:
\begin{align}
   N(p, E) {\rm d}p {\rm d}E = &t_{\rm obs} \int_{E_{\rm true}} \int_{p_{\rm true}}  R(p, E|p_{\rm true}, E_{\rm true})\\
   &\times \Phi(p_{\rm true}, E_{\rm true}) {\rm d}E_{\rm true} {\rm d}p_{\rm true}
\end{align}
where
\begin{itemize}
\item $R(p, E| p_{\rm true}, E_{\rm true})$ is the instrument response
\item $\Phi(p_{\rm true}, E_{\rm true})$ is the parametrised sky flux model
\item $t_{\rm obs}$ is the observation time
\end{itemize}

@@

\gammaray data at the Data Level 3 (DL3) therefore consists in lists of gamma-like events and their
corresponding instrument response functions (IRFs). The latter include the aforementioned
effective area, point spread function (PSF), energy dispersion and residual hadronic background.
The handling of DL3 data is performed by classes and methods
in the \code{gammapy.data} (see Section~\ref{ssec:gammapy-data}) and the \code{gammapy.irf}
(see Section~\ref{ssec:gammapy-irf}) subpackages.

@@

The next step of the analysis is the data reduction, where all observation events and instrument
responses are filled into or projected onto a common physical coordinate system, defined by
a map geometry. The definition of the map geometry typically consists of a spectral dimension
defined by a binned energy axis and of a spatial dimension, which either defines 
a spherical projection from celestial coordinates to an pixelised image space
(for 3-dimensional or cube analysis) or a region on the sky (for regular spectral analysis).
The \code{gammapy.maps} subpackage provides general multidimensional geometry objects
(\code{Geom}) and the associated data structures (\code{Maps}) (see Section~\ref{ssec:gammapy-maps}).

>>>>

\subsection{Events and Instrument Response Functions: the Data Level 3}

\gammaray data at the Data Level 3 (DL3) consists in lists of gamma-like events and their
corresponding instrument response functions (IRFs). The latter include the effective area,
point spread function (PSF), energy dispersion and residual hadronic background.

In the most general way we can write the expected number of detected events from a given astrophysical source
of \gammaray at measured position $p$ and energy $E$:
\begin{align}
   N(p, E) {\rm d}p {\rm d}E = &t_{\rm obs} \int_{E_{\rm true}} \int_{p_{\rm true}}  R(p, E|p_{\rm true}, E_{\rm true})\\
   &\times \Phi(p_{\rm true}, E_{\rm true}) {\rm d}E_{\rm true} {\rm d}p_{\rm true}
\end{align}
where
\begin{itemize}
\item $R(p, E| p_{\rm true}, E_{\rm true})$ is the instrument response
\item $\Phi(p_{\rm true}, E_{\rm true})$ is the parametrised sky flux model
\item $t_{\rm obs}$ is the observation time
\end{itemize}

@@

An additional component of DL3 IRFs is the residual hadronic background model $$.
It represents the  intensity of mis-identified charged particles events that are expected
during an observation. It is defined as a function of the measured position in the field-of-view
and measured energy.

In total, the expected number of events in a \gammaray observation is given by:
\begin{align}
N(p, E) {\rm d}p {\rm d}E =  E_{\rm disp} \star (PSF \star A_{\rm eff} t_{\rm obs} t_{\rm obs}) + Bkg(p, E)
\end{align}

\subsection{Data analysis workflow}

In Gammapy, the handling of DL3 data is performed by classes and methods
in the \code{gammapy.data} (see Section~\ref{ssec:gammapy-data}) and the \code{gammapy.irf}
(see Section~\ref{ssec:gammapy-irf}) subpackages.

@@

The next step of the analysis is the data reduction, where all observation events and instrument
responses are filled into or projected onto a common physical coordinate system, defined by
a map geometry. The definition of the map geometry typically consists of a spectral dimension
defined by a binned energy axis and of spatial dimensions, which either define 
a spherical projection from celestial coordinates to a pixelised image space
(for 3-dimensional or cube analysis) or a region on the sky (for regular spectral analysis).
The \code{gammapy.maps} subpackage provides general multidimensional geometry objects
(\code{Geom}) and the associated data structures (\code{Maps}) (see Section~\ref{ssec:gammapy-maps}).
